\documentclass[letterpaper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{multirow}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{array}
\usepackage{nth}
\usepackage{makecell}
\usepackage{pdflscape}
\usepackage{url}
\usepackage[autostyle=try]{csquotes}

%Hyperlink Fix
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=red,urlcolor=Maroon,breaklinks=true]{hyperref}


\renewcommand\theadalign{tl}

\newcolumntype{P}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\newcommand\Tstrut{\rule{0pt}{2.6ex}}         % = `top' strut
\newcommand\Bstrut{\rule[-0.9ex]{0pt}{0pt}}   % = `bottom' strut

\begin{document}

\scriptsize

%{\def\arraystretch{2}\tabcolsep=10pt
\begin{longtable}{P{.25\linewidth} P{.15\linewidth} P{.25\linewidth} P{.25\linewidth} P{.3\linewidth}}
\caption{Add Health variable definitions and codings}
\label{tab:appendix_data_addhealth} \\

\hline
\textbf{Description}  & \textbf{Variable} & \textbf{Survey Question} & \textbf{Formula} \Bstrut\\
\hline
\endfirsthead

\caption{Add Health variable definitions and codings} \\

\hline
\textbf{Description}  & \textbf{Variable} & \textbf{Survey Question} & \textbf{Formula} \Bstrut\\
\hline
\endhead

\hline
\endfoot
 
\hline
\endlastfoot

\hline
Interview month & 
imonth &
N/A &
N/A \Tstrut\\

Interview year & 
iyear &
N/A &
N/A \Tstrut\\

Birth month & 
bmonth &
N/A &
N/A \Tstrut\\

Birth year & 
byear &
N/A &
N/A \Tstrut\\

Sex & 
bio\_sex &
N/A &
N/A \Tstrut\\

Pseudo state identifier & 
w1state; w2state &
N/A &
\enquote{State} = w1state if iyear = 95; \enquote{State} = w2state if iyear = 96 \Tstrut\\

Sample weight & 
gswgt1; gswgt2 &
N/A &
\enquote{Weight} = gswgt1 if iyear = 95; \enquote{Weight} = gswgt2 if iyear = 96 \Tstrut\\

Race & 
h1gi6a &
What is your race? &
White (= 1) \Tstrut\\

Driver's license & 
h1ee10; h2ee10 &
Do you have a valid driver's license (not a driver's permit)? &
Yes (= 1) \Tstrut\\

Vehicle miles driven (baseline) & 
h1ee11; h2ee11 &
About how many miles do you drive each week? &
0 (= 1); 25 miles (= 2); 75 miles (= 3); 150 miles (= 4)  \Tstrut\\

Vehicle miles driven (alternate) & 
h1ee11; h2ee11 &
About how many miles do you drive each week? &
0 (= 1); 25 miles (= 2); 75 miles (= 3); 265 miles (= 4)  \Tstrut\\

Work for pay & 
h1ee3; h2ee3 &
In the last 4 weeks, did you work---for pay---for anyone outside your home? This includes both regular jobs and things like baby-sitting or yard work. &
Yes (= 1) \Tstrut\\

Not enrolled nor graduated & 
h1gi21; h2gi10 &
Why aren't/weren't you going to school? &
For any reason other than graduation (= 1, 2, 3, 5 or 6 if iyear = 95; = 1, 2, 3, 4, 5, 7 or 8 if iyear = 96) \Tstrut\\

\end{longtable}
\begin{flushleft}
\scriptsize Notes: This table lists the codings and definitions from Wave I (1995) and Wave II (1996) of Add Health that were used in the analysis. Responses were coded as missing if the respondent answered ``don't know'' or ``refused'' to a question. Detailed survey documents are available at: \mbox{\url{https://www.cpc.unc.edu/projects/addhealth/documentation/restricteduse/datasets}}.
\end{flushleft}

%}

\end{document}
